Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
r nids

The Fogo Island archipelago, off the coast of Newfoundland, Canada, is home to
approximately 300 woodland caribou. During routine fieldwork on May 30, 2017, we
observed an unmarked adult male caribou swim between Western and Eastern Indian
Islands (Figure 1), a distance of at least 470 m which took ~9 minutes (~52 m per
minute). This observation prompted us to investigate whether swimming behaviour
was common among GPS radio-collared caribou in the population (n = 29 adult
females; 1240g, GPS 4400M; Lotek Wireless Inc., Newmarket, Ontario, Canada). We
identified swimming events as two consecutive GPS (2-hour relocation rates)
locations from an individual occurred on different islands. Northeastern
Newfoundland typically experiences pack ice during winter and caribou are known
locally to travel between islands by walking over the ice. We restricted our GPS
data to the ice-free period of the year (April 1 - December 31) <!--confirm dates
--> and we identified 12 adult female caribou that collectively had XX
swimming events over three years (Figure 2). In addition to our own visual and
remotely sensed observations, residents of Fogo Island have also reported
observing caribou swimming between islands on numerous occasions.

>>>>

The Fogo Island archipelago, off the coast of Newfoundland, Canada, is home to
approximately 300 woodland caribou. During routine fieldwork on May 30, 2017, we
observed an unmarked adult male caribou swim between Western and Eastern Indian
Islands (Figure 1), a distance of at least 470 m which took ~9 minutes (~52 m
per minute). This observation prompted us to investigate whether swimming
behaviour was common among GPS radio-collared caribou in the population (n = 29
adult females; 1240g, GPS 4400M; Lotek Wireless Inc., Newmarket, Ontario,
Canada). We identified swimming events as two consecutive GPS (2-hour relocation
rates) locations from an individual occurred on different islands. Northeastern
Newfoundland typically experiences pack ice during winter and caribou are known
locally to travel between islands by walking over the ice. We restricted our GPS
data to the ice-free period of the year (April 1 - December 31) and we
identified  adult female caribou that collectively had `r nids` swimming events
over three years (Figure 2). In addition to our own visual and remotely sensed
observations, residents of Fogo Island have also reported observing caribou
swimming between islands on numerous occasions.
